---
title: "Long Pond Monitoring Report 2025"
author: "Evan Krause"
format: html
editor: visual
tabsets: true
toc: true
toc-location: left
toc-title: "Table of Contents"
toc-depth: 2
---

```{r, echo=F, warning=FALSE, message=FALSE}

library(tidyverse)
library(gtsummary)
library(GGally)
library(gt)

source("lp_report_25_files/lp_clean.r")
```

# Introduction

This report summarizes the water quality monitoring activities performed by DCR-DWSP staff from May to September 2025.

## Site description

Long Pond is a 177-acre great pond in Rutland, Massachusetts (71°58’45”W, 42°26’55”N) consisting of three basins of varying depths and acreages that are connected by navigable waterways. The area in and around Long pond is owned and managed by DCR-DWSP. There are no actively used man-made structures in the areas directly abutting water body. Use of the water body is restricted to shore fishing and boating, though boating using motors greater than 25 horsepower (hp) is restricted to the period between Memorial Day and Labor Day.

# Methods

## Measured quality parameters and associated units

| **Parameter**        | **Unit**                     |
|----------------------|------------------------------|
| Depth                | Meters                       |
| Temperature          | Degrees Celsius              |
| Dissolved Oxygen     | Percent                      |
| Specific conductance | microsieverts per centimeter |
| pH                   | pH                           |
| Turbidity            | FNU                          |
| Phycocyanin          | micrograms per liter         |
| Chlorophyll-a        | milligrams per liter         |

# Results

## Parameter summary table

```{r}

```

## Profiles

::: panel-tabset
### 05-15-25

### 06-22-25

### 07-15-25
:::

```{r}
1 + 1
```

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
