---
title: "Pond monitoring functions"
author: "Evan Krause"
format: html
editor: visual
---

# Long pond and holding pond monitoring functions

This document serves as a reference for functions used in the processing of data collected from Long Pond in Rutland, MA and the Quabbin holding ponds, Pottapaug and O'laughlin

```{r, echo=FALSE, warning=FALSE, collapse=TRUE, message=FALSE}
remove(list = ls()) #removes all prior environment variables

pkg <- c( #place additional necessary packages here
   "tidyverse"
 )
 
 
 installed_packages <- pkg %in% rownames(installed.packages()) #check if necessary packages are installed
 if (any(installed_packages == FALSE)) {
   install.packages(pkg[!installed_packages]) #install if not in installed_packages list
 }
 invisible(sapply(pkg, library, character.only = TRUE)) #call library across pkg list
remove(pkg,installed_packages)
```

## CSV cleaning function {#sec-csv-cleaning-function}

This function,

1.  Imports a .csv file from the "data" folder in the respective working directory
2.  Coerces most character columns to factors
3.  Coerces the "Date" column to a Date-class, moves to the first position, and removes the prior "Date" column.
4.  Renames columns 2:16 into lowered camel_case for ease of use in EDA
5.  Relocates the field representing vertical position as the first numeric parameter column

```{r}
clean_csv <- function(file) {
  raw <- readr::read_csv(here::here("data", file))
  
  raw <- raw |> dplyr::mutate(dplyr::across(tidyselect::where(is.character), as.factor),
                              date = lubridate::mdy(Date)) |>
    dplyr::relocate(date, .before = tidyselect::everything()) |>
    dplyr::select(-Date) |>
    dplyr::rename(
      time = 2,
      site = 3,
      unit = 4,
      user = 5,
      temp = 6,
      do_pct = 7,
      do_mgl = 8,
      spc_us = 9,
      ph = 10,
      fnu = 11,
      pcya_rfu = 12,
      pcya_ugl = 13,
      chl_rfu = 14,
      chl_ugl = 15,
      vpos_m = 16
    ) |>
    dplyr::relocate(vpos_m, .after = user)
}
```

Usage of this function should be in the format below:

```{r, message=FALSE,eval=TRUE}
data <- clean_csv("05082025_EXO11_LP_Profile.csv")
```

This function should result in the creation of a dataframe of the form illustrated below:

```{r}
head(data, n = 5)
```
